\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins

\usepackage{tabularx}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Muppidi Rahul Reddy} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{+1(940) 745-9717 \\ Sunnyvale, CA, 94085
\\ \href{mailto:rahulreddy3620@gmail.com}{rahulreddy3620@gmail.com} \\ \href{https://www.linkedin.com/in/muppidi-rahul-reddy/}{linkedin.com/in/muppidi-rahul-reddy/}}
\\ \href{https://www.github.com/RahulReddy20}{github.com/RahulReddy20}
\\ \href{https://www.rahul-reddy.vercel.app}{rahul-reddy.vercel.app}}

% \href{www.faangpath.com}{www.faangpath.com} %

\begin{document}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Master of Science in Computer Science},  \hfill {Aug 2022 - Dec 2023}\\
The University Of Texas at Dallas {\hfill{\bf GPA - 3.43}} \\
\textbf{Relevant Coursework:} Statistical Methods for Data Science, Machine Learning, Computer Vision, Big Data Analytics, Design and Analysis of Algorithms, Web Programming Languages, Database Design.

{\bf Bachelor of Technology in Information Technology}, \hfill {Jul 2018 - May 2022} \\
Indian Institute Of Information Technology, Allahabad   \\
\textbf{Relevant Coursework:} Statistical Methods for Data Science, Machine Learning, Computer Vision, Big Data Analytics
% Minor in Linguistics \smallskip \\
% Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\end{rSection}

%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}

\noindent % Ensure table aligns with text block margin
\begin{tabularx}{\textwidth}{ @{} >{\bfseries}l @{\hspace{3ex}} X } % Table spans \textwidth, X column wraps
Programming Languages & Python, Java, JavaScript, C/C++, R, Shell Scripting \\
Databases & MySQL, PostgreSQL, MongoDB, Oracle DB \\
Cloud \& Big Data & AWS (S3, EC2, RDS, Lambda, Textract, OpenSearch Service, SageMaker, Bedrock), Apache Spark, Hadoop, Kafka \\
Web Development & HTML, CSS, React, NextJS, PHP, Typescript, Flask \\
Machine Learning & PyTorch, TensorFlow, Pandas, NumPy, Scikit-learn, SciPy, YOLOv5, Keras \\
Generative AI & LLMs, LangChain, LMStudio, Ollama, Prompt Engineering, RAG \\
Other Tools \& Technologies & Docker, Git, Power BI, MATLAB, Excel, MLflow \\
\end{tabularx}
\end{rSection}

\begin{rSection}{EXPERIENCE}

\textbf{Machine Leaning Intern} \textbf{- Pytorch, YOLOv5, Python} \hfill Dec 2021 - Jul 2022\\
Coral Innovations Pvt. Ltd  \hfill {Hyderabad, India}
 \begin{itemize}
    \itemsep -6pt {} 
     \item Developed the Meter Board reader which is a core element in the product’s design, the product is an application which reads the meter reading from the images taken and interprets the data according to requirements.
     \item Introduced tools to clean and group the dataset using python and Yolov5 which in turn enhances the efficiency and save time of other employees by \textbf{30\%}.
    \item Built a Yolo v5 model on images from end to end and trained it to suit the requirement. And was successful in getting predictions of nearly\textbf{ 78\%}.  
 \end{itemize}


\end{rSection} 

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}
\vspace{-1.25em}
\item \textbf{Abstractive Text Summarization Using Natural Language Processing - } \textbf{Python, Pytorch} 
\begin{itemize}
    \itemsep -6pt {} 
     \item Collaborated on enhancing Text Summarization using Python and PyTorch, applying the JEANS (Joint Entity and Summary Generation) approach alongside the BART model.
     \item The focus remained on preserving factual consistency rather than replicating original outputs.
 \end{itemize}
 
\item \textbf{Semantic Segmentation Of Satellite Imagery Using CNN} \textbf{- Python, Tensorflow} 
\begin{itemize}
    \itemsep -6pt {} 
     \item Programmed and crafted a satellite imagery Semantic Segmentation framework in Python with TensorFlow.
     \item Objects were extracted into three classes from aerial images using the Softmax activation function, model averaging, and CNN, resulting in an impressive accuracy range of {\bf91-95\%}.
 \end{itemize}

\item \textbf{Preictal And Interictal Seizure Classification Using Spectrogram And CNN Techniques} \textbf{- Python, Tensorflow, Keras}  
\begin{itemize}
    \itemsep -6pt {} 
     \item Designed a classification system for pre-ictal and inter-ictal seizures, critical in epilepsy treatment.
     \item  Utilized Python, TensorFlow, and Keras to employ spectrograms for data representation and applied CNN to build the model, achieving an accuracy rate of approximately {\bf89.3\%}.
     
 \end{itemize}
 
\end{rSection} 

%----------------------------------------------------------------------------------------
\begin{rSection}{Personal Accomplishments} 
\vspace{0em}
\begin{itemize}
    \itemsep -6pt {} 
     \item Maintained all social media platforms and produced announcements for the Dance Crew.
     \item Helped coordinate several programs and activities to increase media platform's engagement with users.
     \item Participated in various hackathons and data science competitions, showcasing my problem-solving skills and technical prowess.
     \item Notable achievements include leading a team to a top-three finish at PRAGMA, where the team developed a customer churn prediction model.
     \item Excelled in a HackAI hackathon challenge by creating a real-time image recognition system.
 \end{itemize}


\end{rSection}

%----------------------------------------------------------------------------------------


\end{document}
